\documentclass[10pt,a4paper]{amsbook}

\usepackage{ucs}
\usepackage[utf8x]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage[italian]{babel}
\usepackage{fontenc}
\usepackage[all]{xy}
\usepackage{graphicx}
\usepackage{prooftree}

\usepackage{hyperref}
\hypersetup{%
    colorlinks=true, linktocpage=true, pdfstartpage=3, pdfstartview=FitV,%
    breaklinks=true, pdfpagemode=UseNone, pageanchor=true,
    pdfpagemode=UseOutlines, plainpages=false, bookmarksnumbered,
    bookmarksopen=true, bookmarksopenlevel=1, hypertexnames=true,
    pdfhighlight=/O,%hyperfootnotes=true,%nesting=true,%frenchlinks,%
    %urlcolor=webbrown, linkcolor=RoyalBlue, citecolor=webgreen,
    %pagecolor=RoyalBlue,%
    % uncomment the following line if you want to have black links (e.g., for
    % printing)
    %urlcolor=Black, linkcolor=Black, citecolor=Black, pagecolor=Black,%
    pdftitle={Dispense di Logica 2},%
    pdfauthor={},%
    pdfsubject={},%
    pdfkeywords={},%
    pdfcreator={pdfLaTeX},%
    pdfproducer={LaTeX with hyperref and classicthesis}%
}

\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
% Define block styles
\tikzstyle{decision} = [diamond, draw, fill=white, 
    text width=3.5em, text badly centered, node distance=2cm, inner sep=0pt]
\tikzstyle{block} = [rectangle, draw, fill=white, 
    text width=5em, text centered, minimum height=2em]
\tikzstyle{line} = [draw, -latex']
\tikzstyle{noblock}=[rectangle,
    text width=5em, text centered, minimum height=2em]

\newcommand{\roundentry}[1]{*++[o][F-] {#1}} 
\newtheorem{esempio}{Esempio}[chapter]
\newtheorem{oss}{Osservazione}[chapter]
\newtheorem{prop}{Proposizione}[chapter]
\newtheorem{defi}{Definizione}[chapter]
\newtheorem{lem}{Lemma}[chapter]
\newtheorem{thm}{Teorema}[chapter]
\newtheorem{extra}{Esercizio}
\newtheorem{nota}{Nota}
\newtheorem{programmi}{Definizione}[section]
\newtheorem{progabaco}[programmi]{Teorema}
\newtheorem{corol}{Corollario}[chapter]


\newenvironment{mylisting}
{\begin{list}{}{\setlength{\leftmargin}{1em}}\item\bfseries}
{\end{list}}

\newenvironment{mytinylisting}
{\begin{list}{}{\setlength{\leftmargin}{1em}}\item\tiny\bfseries}
{\end{list}}

\title{Dispense di Logica 2}
\author{}
\date{}

\begin{document}

\maketitle

\tableofcontents

\include{01_turing_registri}
\include{02_programmi_ricorsive}
\include{03_insiemi_re}
\include{04_ha}
\include{05_rappresentabilita}
\include{06_aritmetizzazione}
\include{07_logica_dimostrabilita}
\include{08_incompletezza_primo}
\include{09_incompletezza_secondo}
\include{10_conseguenze}

\begin{thebibliography} {}
\bibitem{Tur} \textsc{Turing}, \textsl{On computable numbers, with an
application to the entscheidungproblem}, 1936: abelard.org.

\bibitem{Stnfrd} \textsc{Online Stanford Enciclopedia}: plato.stanford.edu.

\bibitem{CompNr} \textsl{Computable Numbers and the Turing Machine}, 1936:
turing.org.uk.

\bibitem{WTM} \textsc{Jack Copeland}, \textsl{What is a Turing Machine?}, 2000:
alanturing.net.

\bibitem{Cut} \textsc{N. Cutland}, \textsl{Computability. An
  Introduction to Recursive Function Theory}, 1980.

\bibitem{Dis} \textsc{Unipd}, \textsl{Dispense del corso di Logica 2},
  2009.
\bibitem{Wik} \textsc{Wikipedia}, \url{http://en.wikipedia.org}.
\bibitem{TK} \textsc{G. Takeuti}, \textsl{Proof Theory}, 1987.

\bibitem{key-1}{[}Hilbert, 18.. D.HILBERT. Ricerche sui fondamenti
della matematica, a cura di V.Michele Abrusci, Bibliopolis, 1984.

\bibitem{key-4}{[}Sambin, 1987 G. SAMBIN. Alla ricerca della certezza
perduta. 

\bibitem{key-5}{[}Cantini, 1979 A. CANTINI. I fondamenti della matematica,
Loescher, 1979.

\bibitem{key-8}{[}Hintikka, 19.. HINTIKKA. On Godel.

\bibitem{key-1}{[}Avigad, 2001 J.AVIGAD \& E.H.RECH. {}``Clarifyng
the nature of infinite'': the development of metamathematics and
proof theory.

\bibitem{key-1}{[}Zach, .... R.ZACH. Hilbert's program then and now.

\bibitem{Boolos} \textsc{G. Boolos}, \textsl{The Logic of Provability}, Cambridge University Press, 1993.

\bibitem{Visser} \textsc{A. Visser}, \textsl{Aspects of Diagonalization and Provability}, PhD thesis, Utrecht, 1981.

\end{thebibliography}

\end{document}
